### 2015-02-13 fundamentals/impl.tex
adds api def
first rough draft of a dre section

The architecture of \Cyclus allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness by protecting the core logic 
from changes in the extensions. 
The researcher can focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features, independent from the team of \Cyclus core developers. 
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. For example, if an analyst would like 
to compare the effect of using different models to determine the input fuel 
composition for fast reactors, a variety of fuel fabrication archetypes can be 
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

@@

\TODO{Matt Gidden, please fill in}

>>>>

The architecture of \Cyclus allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. To achieve this, agents are developed using the \Cyclus framework \gls{API}, a set of functions and protocols
which 
assist in agent development and specify how agents should be defined. 
This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness by protecting the core logic 
from changes in the extensions. 
The researcher can focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features, independent from the team of \Cyclus core developers. 
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. For example, if an analyst would like 
to compare the effect of using different models to determine the input fuel 
composition for fast reactors, a variety of fuel fabrication archetypes can be 
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

@@

Dynamic Resource Exchange (DRE) is the critical resource-related process on
which \Cyclus simulations are built. It defines the resource interaction
mechanisms and methodologies for all agents. As the \Cyclus supply-demand
resolution framework, the DRE must be able to support arbitrary
facilities. Supporting the general \Cyclus philosophy, facilities are treated as
black boxes and a clear supply-demand communication framework is defined.

The DRE consists of three steps: supply-demand information gathering, resource
exchange solution, and trade execution. Importantly, each step is agnostic with
respect to the exchange of resources in question, i.e., the same procedure is
used for both Materials and Products. The information-gathering step consists of
three phases. First, consumers of commodities denote both the quantity of a
commodity they need to consume as well as the target isotopics, or quality, by
posting their demand to the market exchange as a series of \textit{requests}. An
optional collection of demand constraints are associated with each collection of
requests. Collections of requests may be grouped together, denoting
\textit{mutual} requests that represent demand for some common purpose. For
example, a reactor may request UOX and MOX fuel mutually, indicating that either
will satisfy its demand for fuel. Suppliers then respond to the series of
requests with a \textit{bid}. A bid supplies a notion of the quantity and
quality of a resource to match a request. Suppliers may add an arbitrary number
of constraints to accomany bids. For example, an enriched UOX supplier may
supply both a natural Uranium and SWU constraint. Any potential resource
transfer may be denoted as \textit{exclusive}. An exclusive transfer must either
be met fully or not at all in order to support concepts such as the the trading
of individual reactor assemblies. Finally, requesting facilities, institutions
and regions may apply \textit{preferences} to each potential request-bid pairing
based on the proposed resource transfer. Therefore, an institution can apply a
higher preference to a partner to which it is congenial; similarly, a region may
negate any transfers of material which have a higher Uranium enrichment than is
allowable.

The DRE may be solved either optimally by a mathematical program or
approximately by a simulation-based heuristic \TODO{cite}. If any trade is
denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
then either a heuristic must be used or exchanges must be respresented as
Mixed-Integer Nonlinear Programs (MILP). If no exclusive trades exist, a Linear
Programming (LP) model may be used. In practice, LPs solve much faster than
MILPs. However, the capability to model both exists in \Cyclus in order to
provide users with the desired level of fidelity.

Trades are initiated by the \Cyclus kernel after a solution to the DRE is
found. The DRE is executed at each time step. Therefore, if a facility's request
for a resource is not met at a given time step, it may offer a request in the
proceeding time step.
